---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## code is a work in process - which is not yet working correctly

[![Build Status](https://travis-ci.org/ttimbers/distransam.svg?branch=master)](https://travis-ci.org/ttimbers/distransam)

### distransam

Randomly samples groups to get equal N's. Takes a data frame, and returns one with equal N's for each group. For unequal sample sizes, it finds the minimum sample size from the smallest group, and randomly selects that number of samples from each group. A single sub-groups can be specified, as can a maximum N value. The returned object is a dataframe, with all the same original columns as the original data frame.

note - that because this package uses dplyr & `%>%` both distransam & dplyr libraries must be loaded

### Installation

```{r installation, eval = FALSE}
devtools::install_github("ttimbers/distransam")
```
  
### Quick demo

Using a subset of the gapminder dataset

```{r}
library(gapminder)
gap92 <- gapminder[gapminder$year == 1992,]
```

Lets randomly sample the gap92 dataframe for countries from each continent, but in doing so, ensure that we get an equal sample size for each continent. 

```{r}
library(distransam)
library(dplyr)
distransam(gap92, 'continent')
```

Another example of where this could be used, is if you had two groupings that you wanted equal random samples from, for example, if you want random samples of equal size from each plate for each strain

```{r}
# make a data frame with worm strain, Petri plate ID, and a measurement
worm_data <- data.frame(c(rep("N2", 5), rep("CB1", 7)), c(rep('a', 2), rep('b', 3), rep('a', 4), rep('b',3)), sample(5:10, 12, replace = TRUE))
colnames(worm_data) <- c('strain', 'plate', 'measurement')

#view data frame
worm_data
```

Use distransam to get a new, randomly sampled dataframe where N's are equal for each plate, and strain:

```{r}
distransam(worm_data, 'strain', 'plate')
```
